Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-03-13 apples_and_oranges.qmd
More tabulating and added bits to method

We conducted a meta-analysis to test for differences between psychotherapy versus medication trials in sample characteristics at baseline.

First, we compared depression severity levels at baseline. In order to compare across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:

@@

We also performed meta-analyses implemented in R's meta package to compare psychotherapy versus medication trials on the gender composition of the sample, mean age, and number of trial sites.

@@

First, for each of the the meta-analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways. First, we excluded studies which recruited participants with subclinical levels of depression. Second, we restricted the analyses to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram. Third, we restricted the metaregression to studies that *did not* use waitlist as their control.

@@

Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline. In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others. All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.

@@

### Gender

Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`). On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% women across medication trials.  Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`). This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Use those ids to subset all dataframes in the list
# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
# So we need to further subset. For the active arms, I am filtering out conditions that do not meet our criteria. 
# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
# We may have multiple controls per study id for this reason, though this isn't a problem conceptually.

@@

Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`). There were no significant differences in mean age between modalities on further sensitivity analyses.

@@

@@

On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was eiter CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`). When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference no longer reached statistical significance (p = `results_met_sev_clin$pval_between`).

@@

# Now lets make a table that combines across these baseline characteristics variables

@@

# For row names
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "Gender",
    row_number() == 4 ~ "Age",
    row_number() == 7 ~ "Severity",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

@@

df_overall_baseline_results %>%
  kbl(caption = "Sample characteristics at baseline") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#D3D3D3",  extra_css = "border-bottom: 2px solid grey;" ) %>% 
  row_spec(c(1, 4, 7), bold = T, extra_css = "border-top: 2px solid grey;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9))

```
### Number of trial sites

@@

df_sites_summary_stats %>%
  kbl(col.names = c("Modality", "N", "Mean", "SD")) %>% 
  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE)

# ### do ALL studies using percentage at baseline
# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
# 
# 
# #turn sds to sec
# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(all_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get CDRS studies
# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
# 
# #turn sds to sec
# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get HAM-D studies
# hamd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
# 
# 
# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
#                                                           %in% hamd_study_ids,]
# 
# hamd_studies_for_baseline_metareg <- list_hamd_study # 
# 
# #turn sds to sec
# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
# 
#

# # Look at the diagnostics of included studies 
# 
# filtered_data <- df_appl_v_orange %>%
#   filter(psy_or_med == 1) %>% 
#   filter(new_study_id %in% cbt_meds_study_ids) %>%
#   distinct(new_study_id, .keep_all = TRUE)
# 
# summary_result <- filtered_data %>%
#   group_by(diagnosis) %>%
#   summarise(count = n())
#

@@

@@

Table 1 summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->

@@

knitr:: kable(df_mean_coefs_from_sim, caption = "Table 1")
```

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
knitr:: kable(aggregate_results_overall, caption = "Table 2", digits = 2
              )
```

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# 
# # plot the mean z for the difference between controls
# z_psy_con_vs_med_con <- 0
# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
#   
# }
# 
# 
# 
# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
# 
# 
# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
#   ggplot(aes(x = n_sims, y = z_value)) +
#   geom_point() +
#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
#                arrow = arrow(length = unit(0.3, "cm")),
#                color = "black") +
#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
#            hjust = -0.1, vjust = 0) +
#   theme_minimal() +
#   labs(
#     x = "Number of Simulations",
#     y = "z-value",
#     title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
#     subtitle = "Results from 1000 simulations with within-group standard errors"
#   )
# stab_sims_adjusted_cohens_d
# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
# stab_sims_adjusted_cohens_d
# dev.off()
#

@@

```{r}
# Plots  -----------------------
# 
# #define groups
# df_long_for_metan <- df_long_for_metan %>%
#   mutate(
#     group = case_when(
#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
#       TRUE ~ NA_character_  
#     )
#   )

# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
# 
# # Plot cohens d per arm
# 
# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
#   geom_point(position = position_jitter(width = 0.2), size = 3) +
#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
#   scale_color_manual(values = group_colors) +
#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
#   theme_minimal() +
#   theme(legend.position = "none")
# 
# # Now look at change scores of percentage transformed variables
# 
# df_long_for_metan <- df_long_for_metan %>% 
#   mutate(perc_change = perc_post_mean - perc_baseline_mean)
# 
# ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
#   geom_point(position = position_jitter(width = 0.2), size = 3) +
#   geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
#   geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
#   scale_color_manual(values = group_colors) +
#   labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
#   theme_minimal() +
#   theme(legend.position = "none")
# 
# # # Plot percentage  baseline means 
# # 
# # ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
# #   geom_point(position = position_jitter(width = 0.2), size = 3) +
# #   scale_color_manual(values = group_colors) +
# #   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
# #   theme_minimal() +
# #   theme(legend.position = "none")
# 
# # Box plots
# 
# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
#   scale_fill_manual(values = group_colors) +
#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
#   theme_minimal() +
#   theme(legend.position = "none")

>>>>

We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including gender, age, and severity of depressive symptoms at baseline. Meta-analyses were implemented using R's meta package.

In order to compare depression severity across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:

@@

We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.

@@

First, for each of the the analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways. First, we excluded studies which recruited participants with subclinical levels of depression. Second, we restricted the analyses to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram. Third, we excluded studies that used waitlist as their control condition.

@@

Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline. In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others. All included trials and the types of treatment controls can be found in Supplementary Table 1.

@@

Table 1 summarises the results from each of the meta-analyses examining sample characteristics at baseline. The summary statistics are provided for each subgroup (i.e. for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences. Full results for each of the sensitivity analyses are included in the Supplementary Materials (Table X - Y).

# Start by looking at demographics at baseline
# Currently we have both control and active conditions, we just need each study once

@@

# Use those ids to subset all dataframes in the list

@@

# Now the no waitlist group

no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id

df_for_gender_metan_no_wl <- df_for_gender_metan %>%
  filter(new_study_id %in% no_wl_ids)

met_perc_women_no_wl <- metagen(TE = percent_women,
                           seTE = percent_women_std_error,
                           studlab = new_study_id,
                           data = df_for_gender_metan_no_wl,
                           sm = "",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies with controls that are not wl",
                           subgroup = psy_or_med,
                           tau.common = FALSE)

# Apply the function to the meta-analysis result
results_met_perc_women_no_wl <- extract_stats(met_perc_women_no_wl)

knitr:: kable(results_met_perc_women_no_wl, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")

```
### Gender

Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`). On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.  Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`). This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).

@@

df_for_age_metan$se_age <- as.numeric(df_for_age_metan$se_age)

@@

Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`). There were no significant differences in mean age between modalities on further sensitivity analyses.

@@

# Now overall
# Lets make a table that combines across these baseline characteristics variables

@@

# For row names
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "Percent Women",
    row_number() == 4 ~ "Age",
    row_number() == 7 ~ "Severity",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

@@

df_overall_baseline_results %>%
  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))

On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`). When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).

@@

df_sites_summary_stats <- df_sites_summary_stats %>%
  rename(
    Modality = psy_or_med,
    N = n,
    Mean = mean_sites,
    SD = sd_sites
  )

df_sites_summary_stats %>%
  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

# ### do ALL studies using percentage at baseline
# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
# 
# #turn sds to sec
# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(all_studies_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get CDRS studies
# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
# 
# #turn sds to sec
# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
#                                                          model_1, condition)
# 
# ### get HAM-D studies
# hamd_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
# 
# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
#                                                           %in% hamd_study_ids,]
# 
# hamd_studies_for_baseline_metareg <- list_hamd_study # 
# 
# #turn sds to sec
# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)

@@

### Number of trial sites

@@

Table X summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->

@@

# Prepare to tabulate

df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("n", .after = "condition")

df_mean_coefs_from_sim %>%
  kbl(caption = "Table X: Summary statistics of the estimated SMDs") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

# Prepare to tabulate

aggregate_results_overall <- aggregate_results_overall %>%
  mutate(across(where(is.numeric), ~round(., 2))) %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition))) %>% 
  relocate("condition", .before = "coefficients")

aggregate_results_overall %>%
  kbl(caption = "Table X: Meta-regression results") %>% 
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
  row_spec(row = 0, background = "#EBEBEB") %>% 
  column_spec(column = 1, border_right = T)

@@

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# 
# # plot the mean z for the difference between controls
# z_psy_con_vs_med_con <- 0
# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
#   
# }
# 
# 
# 
# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
# 
# 
# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
#   ggplot(aes(x = n_sims, y = z_value)) +
#   geom_point() +
#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
#                arrow = arrow(length = unit(0.3, "cm")),
#                color = "black") +
#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
#            hjust = -0.1, vjust = 0) +
#   theme_minimal() +
#   labs(
#     x = "Number of Simulations",
#     y = "z-value",
#     title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
#     subtitle = "Results from 1000 simulations with within-group standard errors"
#   )
# stab_sims_adjusted_cohens_d
# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
# stab_sims_adjusted_cohens_d
# dev.off()

@@

### Supplement

```{r}

# Tables for baseline comparisons

# Gender first

# Now overall
# Lets make a table that combines across these baseline characteristics variables

# For row names
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "Percent Women",
    row_number() == 4 ~ "Age",
    row_number() == 7 ~ "Severity",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

df_overall_baseline_results %>%
  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
  row_spec(row = 1, bold = T) %>% 
  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))

# Plots  -----------------------

#define groups
df_long_for_metan <- df_long_for_metan %>%
  mutate(
    group = case_when(
      psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
      TRUE ~ NA_character_
    )
  )

group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")

# Plot cohens d per arm

ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
  theme_minimal() +
  theme(legend.position = "none")

# Plot percentage baseline means

ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
  theme_minimal() +
  theme(legend.position = "none")

# Box plot Cohens d by group

ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
  scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
  geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
  geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
  scale_fill_manual(values = group_colors) +
  labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
  theme_minimal() +
  theme(legend.position = "none")
